Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-14 Ben_Manuscripts/structure_paper/Draft.tex
More edits

  We used the equilibrated parallel displaced system in the ordered pore basin
  to calculate ionic conductivity since its structure is the closest match to
  experiment. The model gives reasonable estimates of ionic conductivity when
  compared to experiment.  We compare calculated values of ionic conductivity
  obtained using the Nernst-Einstein relation and Collective Diffusion model in
  Figure~\ref{fig:conductivity}. The two methods agree with each other within
  error, although the uncertainty obtained using the Collective Diffusion model
  is much higher. We require much longer simulations to lower the uncertainty,
  however it is not feasible to do so with a large system. We will only use the
  Nernst-Einstein relation in future calculations of this type.

@@

  \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{IC_offset.png}
        \caption{The collective diffusion model and the nernst-einstein relation yield
        agreeing values of ionic conductivity. Both methods give calculated
        values of ionic conductivity an order of magnitude higher than the experimental
        value.}
        \label{fig:conductivity}
  \end{figure}

@@

  Evidence strongly supports that monomers stay partitioned into layers which
  stack to create pores and that each layer contains 5 monomers. We see periodic
  spacing of layers based on the z-direction correlation function, $g(z)$, of
  atoms in the tails and separately of atoms in the head groups. Systems not
  built with 5 monomers per layer result in assemblies whose pore-to-pore spacing
  is inconsistent with experiment.

  We have explored the affect of two different $\pi$-$\pi$ stacking modes on
  the equilibrated membrane structure. Simulated diffraction patterns generated
  from MD trajectories suggest that the parallel-displaced configuration produces
  a structure with the closest match to experiment.

  We have observed a number of metastable configurations. We witnessed
  long-term stability of systems built with a varied number of monomers per layer
  as well as in different $\pi$-$\pi$ stacking configurations. We also examined
  how the structure changes based on the initial distance between layers and
  showed how systems differ when built with layers spaced 5~\AA~versus
  3.7~\AA~apart. The configuration that showed the greatest agreement with
  experiment was built in the parallel-displaced configuration, with 5 monomers
  per layer and an initial layer spacing of 3.7 \AA.

  We characterized the environment centered around the membrane pores and
  learned that the pores are generally filled by monomer head groups and sodium
  ions. Membranes prepared in the sandwiched configuration have lower density 
  pores. We also observed that there is not a hard partition between hydrophlic
  and hydrophilic regions, rather there is a gradient.  This finding has raised
  questions about the nature of any size-exclusion separations.

  We learned that we do not need water to create well-defined pore structures.
  Systems whose pores were filled with varying amounts of water showed a decrease
  in structuring relative to dry systems.

@@

%MRS6'' isn't it 1-3 orders of magnitude lower? You cite some slower statistics, and there might be differences between lyotrpic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
  We acknowledge that our simulated system exhibits glassy dynamics. The
  measured diffusion constants of monomers are three orders of magnitude lower
  than expected. It is possible that our equilibration procedure induces these
  types of metastable phases. It is also possible that the observed dynamics are
  characteristic of the real system. We took great care to overcome the potential
  limitations of our equilibration procedure and have come up with a structure
  that is in good agreement with experimental data.

>>>>

  We used equilibrated systems in the ordered pore basin to calculate ionic 
  conductivity since we believe its structure is the closest match to
  experiment. Our models give reasonable estimates of ionic conductivity when
  compared to experiment. We compare calculated values of ionic conductivity
  obtained using the Nernst-Einstein relation and Collective Diffusion model in
  % names of equations capitalized?
  Figure~\ref{fig:conductivity}. The two methods agree with each other within
  error, although the uncertainty obtained using the Collective Diffusion model
  is much higher. We require much longer simulations to lower the uncertainty,
  however it is not feasible to do so with a large system. We will only use the
  Nernst-Einstein relation in future calculations of this type.

@@

  \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
        \caption{The Collective Diffusion model and the nernst-einstein relation yield
        agreeing values of ionic conductivity for both systems simulated. Both methods
        estimate the value of the ionic conductivity to be an order of magnitude higher 
        than the experimental value.}
        \label{fig:conductivity}
  \end{figure}

@@

  We observed a number of metastable configurations, stable for hundreds of 
  nanoseconds, which do not fit the experimental profile we have tried to match. 
  We explored two classes of metastable basins which are dependent on the initial
  vertical stacking distance between monomers : the ordered and disordered pore basins.
  We expect that these metastable configurations will eventually rearrange and converge
  to a single equilibrium structure. We conducted extensive analysis in order to 
  isolate structures which most closely resembles the true equilibrium structure.

  The system's pore spacing is most consistent with experiment when systems
  are built with 5 columns per pore. The distance between pores increases with the 
  number of columns per pore. Pores pack closer together in the disordered pore 
  basin. Systems built with 6 columns per pore in the disordered basin expand in 
  the z-direction which suggest that it may rearrange to 5 columns per pore long term.

  We have maximized our model's consistency with the experimental WAXS pattern. We show
  that R-alkanes and R-pores appear where expected. We learned that R-spots is likely 
  due to ordered alkane chain packing. R-$\pi$ appears at lower q values than experiment
  because monomer stack too far apart. We found that our model cannot reproduce R-double, 
  however we have come up with a three different mechanisms that lead to the reflection's
  appearance. The most likely explanation is that monomers within each column rotate ca.
  15\degree with respect to their vertically adjacent neighbors so that tails can pack 
  together more tightly.

  We characterized the environment centered around the membrane pores and
  learned that the pores are generally filled with monomer head groups and sodium
  ions. All systems studied showed a similar distribution of sodium, head groups 
  and tails, which means we can study solute transport in any of the systems here
  and extract similar transport mechanisms. We also observed that there is not a 
  hard partition between hydrophlic and hydrophilic regions, rather there is a 
  gradient. This finding has raised questions about the nature of size-exclusion separations.

  We learned that we do not need water to create well-defined pore structures.
  Systems whose pores were filled with varying amounts of water showed a decrease
  in structuring relative to dry systems. At higher water concentrations, the pores
  begin to swell, which may be more conducive to transport.

@@

%MRS6'' isn't it 1-3 orders of magnitude lower? You cite some slower statistics, and there might be differences between lyotrpic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
%  We acknowledge that our simulated system exhibits glassy dynamics. The
%  measured diffusion constants of monomers are one to three orders of magnitude lower
%  than expected. It is possible that our equilibration procedure induces these
%  types of metastable phases. It is also possible that the observed dynamics are
%  characteristic of the real system. We took great care to overcome the potential
%  limitations of our equilibration procedure and have come up with a structure
%  that is in good agreement with experimental data.
